Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-05-14 mtjournal.tex
small changes from Mari's e-mail

\begin{document}
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting {HTER} improvements with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
%s\date{May 10, 2009}

@@

Currently, the most popular evaluation measures include a measure
based on $n$-gram precision known as BLEU \cite{papineni02bleu}) and
the edit-distance measure Translation Edit Rate (TER)
\cite{snover06ter}.  Recent research has found that these measures may
not accurately track translation quality both empirically
\cite{charniak03syntaxlmmt} and theoretically
\cite{callisonburch06bleuproblems}.

@@

\item[Confidence of $n$-best list.] An expectation requires a

@@

\item[Score combination.]: We consider three possible methods for

@@

%% MO: Okay, but a little hard to figure out.
When reporting HTER correlations per-sentence, we use length-weighted
correlation, since unweighted correlations effectively puts too much
emphasis on short sentences.  We do not weight for length for the
per-document correlations in section~\ref{sec:hter1}, because we
assume documents to be equally important (regardless of length).

@@

We train a model using features from one or more of the following
sets:
\begin{description}
\item[E]: the fully syntactic features from the DPM family.
  Specifically, this featureset includes precision and recall scores
  for the $dl$, $lh$, $dlh$, and $dh$ decompositions of the syntactic
  structure, using $n=50$ and $\gamma=0.25$.  The \textbf{E} set
  includes 8 features.
\item[N]: the non-syntactic features from the DPM family;
  specifically, precision and recall for $1g$ and $2g$ decompositions.
  The \textbf{N} set includes 4 features.
\item[T]: the features from basic TERp, which include a separate cost
  for each of insertions, deletions, substitutions, shifts, and
  synonym-alignment. The \textbf{T} set includes 7 features.
  % MO  (to Matt): is this basic TER or basic TERp?
  % TO DO: what are the other two?
\item[P]: features from the automatically-derived TERp paraphrase
  table (4 features) % TO DO: Matt, what are these
\item[B]: two ``length penalties'' one is assigned the count of
  hypothesis words beyond the count of reference words, and one
  assigned the count of reference words beyond the count of hypothesis
  wordsbrevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref).
  % MO: out of curiosity, why do you need 2 features?
  We assign two features here to let the system separately penalize
  ``too short'' translations and ``too long''.
\end{description}

>>>>

\begin{document}
\begin{article}
\begin{opening}         
\title{Expected Dependency Pair Match:\\
Predicting translation quality with expected syntactic structure} 
\author{Jeremy G. \surname{Kahn}\email{jgk@u.washington.edu}}  
\institute{University of Washington}
\author{Matthew \surname{Snover}\email{snover@cs.umd.edu}}
\institute{University of Maryland}
\author{Mari \surname{Ostendorf}\email{ostendor@u.washington.edu}}  
\institute{University of Washington}
\runningauthor{Kahn, Snover \& Ostendorf}
\runningtitle{Expected Dependency Pair Match}
%s\date{May 10, 2009}

@@

Currently, the most popular evaluation measures include a measure
based on $n$-gram precision known as BLEU \cite{papineni02bleu} and
the edit-distance measure Translation Edit Rate (TER)
\cite{snover06ter}.  Recent research has found that these measures may
not accurately track translation quality both empirically
\cite{charniak03syntaxlmmt} and theoretically
\cite{callisonburch06bleuproblems}.

@@

\item[Confidence of $n$-best hypotheses.] An expectation requires a

@@

\item[Score combination.] We consider three possible methods for

@@

%% MO: Okay, but a little hard to figure out.
When reporting HTER correlations per-sentence, we use length-weighted
correlation, since unweighted correlations effectively put too much
emphasis on short sentences.  We do not weight for length for the
per-document correlations in section~\ref{sec:hter1}, because we
assume documents to be equally important (regardless of length).

@@

We train a model using features from one or more of the following
sets:
\begin{description}
\item[E]: the fully syntactic features from the DPM family.
  Specifically, this feature set includes precision and recall scores
  for the $dl$, $lh$, $dlh$, and $dh$ decompositions of the syntactic
  structure, using $n=50$ and $\gamma=0.25$.  The \textbf{E} set
  includes 8 features.
\item[N]: the non-syntactic features from the DPM family;
  specifically, precision and recall for $1g$ and $2g$ decompositions.
  The \textbf{N} set includes 4 features.
\item[T]: the features from basic TERp, which include a separate cost
  for each of insertions, deletions, substitutions, shifts, and
  synonym-alignment. The \textbf{T} set includes 7 features.
  % MO  (to Matt): is this basic TER or basic TERp?
  % TO DO: what are the other two?
\item[P]: features from the automatically-derived TERp paraphrase
  table (4 features) % TO DO: Matt, what are these
\item[B]: two ``length penalties'' one is assigned the count of
  hypothesis words beyond the count of reference words, and one
  assigned the count of reference words beyond the count of hypothesis
  wordsbrevity/prolixity (2 features: one for longer-than-ref, one for
  shorter-than-ref).
  % MO: out of curiosity, why do you need 2 features?
  We assign two features here to let the system separately penalize
  ``too short'' translations and ``too long''.
\end{description}
